Stage 1 Registered Report: The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-05 article.tex
Should I?

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item expected speciation completion time (from Etienne & Rosindell 2012)
  \item expected duration of speciation (from Etienne & Rosindell 2012)
  \item number of taxa in incipient species tree (also: number of subspecies)
  \item would there be a difference in brach lengths between the two sampling methods?
  \item number of taxa in species tree (also: number of species)
  \item mean nLTT statistic
  \item median nLTT statistic
  \item lower bound of 95\% HPD value of nLTT statistic
  \item upper bound of 95\% HPD value of nLTT statistic
  \item 11 ESSes of all parameters estimated by BEAST2:
  \begin{enumerate}  
    \item posterior
    \item likelihood 
    \item prior 
    \item treeLikelihood 
    \item TreeHeight 
    \item BirthDeath 
    \item BDBirthRate 
    \item BDDeathRate 
    \item logP.mrca 
    \item mrcatime 
    \item clockRate
  \end{enumerate}
  \item [some] MCMC operator acceptances
\end{itemize}

>>>>

\begin{itemize}  
  \item 12 simulation parameters:
  \begin{enumerate}  
    \item speciation initiation rate
    \item speciation completion rate
    \item extinction rate
    \item crown age
    \item crown age sigma
    \item sampling method
    \item mutation rate
    \item sequence length
    \item mcmc length
    \item tree sim rng seed
    \item alignment rng seed
    \item beast2 rnd seed
  \end{enumerate}
  \item [NOTE: add yes/no?] expected speciation completion time (from Etienne & Rosindell 2012)
  \item [NOTE: add yes/no?] expected duration of speciation (from Etienne & Rosindell 2012)
  \item number of taxa in incipient species tree (also: number of subspecies)
  \item [NOTE: add yes/no?] would there be a difference in brach lengths between the two sampling methods?
  \item number of taxa in species tree (also: number of species)
  \item mean nLTT statistic
  \item median nLTT statistic
  \item lower bound of 95\% HPD value of nLTT statistic
  \item upper bound of 95\% HPD value of nLTT statistic
  \item 11 ESSes of all parameters estimated by BEAST2:
  \begin{enumerate}  
    \item posterior
    \item likelihood 
    \item prior 
    \item treeLikelihood 
    \item TreeHeight 
    \item BirthDeath 
    \item BDBirthRate 
    \item BDDeathRate 
    \item logP.mrca 
    \item mrcatime 
    \item clockRate
  \end{enumerate}
  \item [some] MCMC operator acceptances
\end{itemize}
